Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-11-10 Talk/Presentation.tex
Added stuff about false positives/negatives and true positives/negatives, also added stuff to the experiments slide.

\subsection{Determining the Accuracy of an Algorithm}
\begin{frame}
  \frametitle{Determining the Accuracy of an Algorithm}
Explain false positive, false negative, true positive, true negative, detection rate.
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Genetic Algorithm Implementation]{Genetic Algorithm Implementation}
\subsection{Algorithm Overview}
\begin{frame}
  \frametitle{Algorithm Overview}

@@

\begin{frame}
	\frametitle{Experiments}
A variety of experiments were run. Two experiments used just RLD09, and three experiments used KDD99 and RLD09 together.

\begin{frame}
	\frametitle{Experiments Using Only RLD09}
Experiment 1

>>>>

\subsection{Determining the Accuracy of an Algorithm}
\begin{frame}
  \frametitle{Determining the Accuracy of an Algorithm}
	\begin{itemize}
		\item False positive (FP): intrusion detection system incorrectly identifies normal activity as being an attack. 
		\item False negative (FN): intrusion detection system fails to identify harmful activity. 
		\item True positive (TP): intrusion detection system correctly identifies activities to be attacks. 
		\item True negative (TN): intrusion detection system correctly
identifies activities to be normal.
		\item Detection rate (DR): the number of true positives divided by the total number of intrusions that happen.
	\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Genetic Algorithm Implementation]{Genetic Algorithm Implementation}
\subsection{Algorithm Overview}
\begin{frame}
  \frametitle{Algorithm Overview}

@@

\begin{frame}
	\frametitle{Experiments}
	\begin{itemize}
		\item A variety of experiments were run. Two experiments used just RLD09, and three experiments used KDD99 and RLD09 together.
		\item The experiments used a total of 16,000 records of normal activity and 10,500 records of attack activity. Of the attack records, 4,000 were denial of service attacks and 6,500 were probe attacks.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Experiments Using Only RLD09}
Experiment 1
\end{frame}
